### 2014-01-23 Draft/approach.tex
Fixed approach into para

The pre-processor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
Finally, the specification extractor then leverages the FOL representation of a sentence to infer specifications.
Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.

Besides the previously described major components the approach also consists of a an external component, namely target specification generator.
This component accepts the specification generated by our approach and using mapping functions to a target specification language generates specifications in the target language of choice.
We next describe each component in detail.

\subsection{API Parser}
\label{sub:parser}

Our API parser accepts the online API documents and extracts method descriptions from it.
In particular, our parser extracts the following fields within method descriptions: 
1) \textit{Summary of the API method},
2) \textit{Summary of request elements of the API method}, and 
3) \textit{Summary of response elements of the method (inclusive of error responses)}.

This step is required to extract the desired descriptive text from the various presentation styles of the API documents.
In particular, different API documents may have different styles of presenting information to developers.
This difference in style may include the difference in the level of detail presented to the developer.
We thus chose very only generic fields that are essential to API methods.

Currently our prototype implementation extracts this information from online \amazon\ only. 
However, almost all of the REST API developer documents are provided online as structured webpages.
Thus, current implementation of parser can be easily extended to extract desired information from any REST API developer documents.

\subsection{Preprocessor}
\label{sub:Preprocessor}

The preprocessor accepts API method descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine.
The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.

>>>>

The preprocessor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
Finally, the specification extractor then leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
Besides the previously described components the approach also consists of a semantic graph generator and type analyzer.
The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by specification extractor component.
The type analyzer components infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
We next describe each component in detail.

\subsection{Preprocessor}
\label{sub:parser}

The preprocessor accepts the API documents and first extracts method descriptions from it.
In particular, the preprocessor extracts the following fields within method descriptions: 
1) \textit{Summary of the API method},
2) \textit{Summary and type information of parameters of the API method}, 
3) \textit{Summary and type information of return values of the method}, and
4) \textit{Summary and type information of exceptions thrown by the methods}.

This step is required to extract the desired descriptive text from the various presentation styles of the API documents.
In particular, different API documents may have different styles of presenting information to developers.
This difference in style may include the difference in the level of detail presented to the developer.
Our approach thus relies on only basic fields that are trivially available for API methods across different presentation styles.

After extracting desired information, the natural language text is further preprocessed to be analyzed by the text-analysis engine.
The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.
